Different centralities in multilayer stream graphs

### 2019-08-07 tex/article/main.tex
commentaires provisoires
Added package for special characters
update articl

%
\subsubsection{Centrality of nodes and the paths}
%
In classical graph, the centrality of the nodes describes how much we encounter a node while browsing a graph. They are different way to browse a graph: the random walk, the contamination models, the shortest path, etc. In the stream graph, the notions are more numerous: we can compute random walks, but with different laws of probabilities of transition, same for the contamination. We can look for the shortest paths (with the less transitions possible) but the fastest paths (the ones that take less time), the foremost paths (the ones that arrives the earliest starting from a certain time), and we can combine those notions.

@@

The {\bf juxtaposed layers} forms a partition of the nodes. For instance, they can model people from different classes in the same school. A relevant way to deal with those layers is to study the interactions between them.

@@

\begin{table}
\begin{tabularx}{\linewidth}{|l|l|X|X|l|l|}
\hline
dataset & Nodes & superimposed aspects  & Juxtaposed aspects & Links & $T$ \\
\hline
High school & Students: 329&  Relationships type (Facebook, Face to face, Friendships) & Sex (F,M,U), Class (9)&  Relationships & 5 days \\
\hline
US planes & Airports: 346 & Companies (17) & - & Flights & 1 month \\
\hline
\end{tabularx}
\caption{Characteristic of the multilayer stream graphs representing our two datasets}
\label{tab:characteristics}
\end{table}

@@

\begin{figure}
\begin{subfigure}{0.45\textwidth}
	\includegraphics[width=\textwidth]{img/planes/intricplanes.pdf}
\end{subfigure}
\begin{subfigure}{0.45\textwidth}
	\includegraphics[width=\textwidth]{img/planes/prVSrw.pdf}
\end{subfigure}
\end{figure}
\subsection{Analysis}
%
\newpage
% ---- Bibliography ----
%
\begin{thebibliography}{6}
%

>>>>

%
\subsubsection{Centrality of nodes and the paths}
%
In classical graph, the centrality of the nodes describes how much we encounter a node while browsing a graph. They are different way to browse a graph. First, it is necessary to define what transistion are possible, depending on the system we model. If the link represent some travels (flights for instance), then to go from one node to another, the``passenge'' has to ``take'' the flight from the beginning to the end. For a relationship multilayer stream graph, something going across the links which represent interaction will be a disease for instance, and can pass from one node to another continuously during the interval of the link.

\textbf{Remarque: illustration possible avec l'image d'un pont-levis ou de ferry-boats pour traverser une rivière}

The random walk gives an information on which nodes are well connected (on the same principle as for the PageRank for classical graphs). The betweenness centrality, computed with shortest paths (in time or transitions) from on node to another, or foremost paths (from one node and one time to another time) allows us to get the node the more important for the connectivity of the other nodes.

@@

The {\bf juxtaposed layers} form a partition of the nodes. For instance, they can model people from different classes in the same school. A relevant way to deal with those layers is to study the interactions between them.

@@

\begin{table}
\begin{tabularx}{\linewidth}{|l|l|X|X|X|l|}
\hline
dataset & Nodes & superimposed aspects  & Juxtaposed aspects & Links & $T$ \\
\hline
High school & Students: 329&  Relationships type (Facebook, Face to face, Friendships) & Sex (F,M,U), Class (9)&  Relationships: 36~732 & 5 days \\
\hline
US planes & Airports: 346 & Companies (17) & - & Flights: 583~986 & 1 month \\
\hline
\end{tabularx}
\caption{Characteristic of the multilayer stream graphs representing our two datasets}
\label{tab:characteristics}
\end{table}

@@

\begin{figure}
\begin{subfigure}{0.45\textwidth}
	\includegraphics[width=\textwidth]{img/planes/intricplanes.pdf}
	\caption{Matrice d'intrication: c'est soit cette matrice, soit la matrice des covariance. Il faut voir laquelle fonctionne le mieux }
\end{subfigure}
\begin{subfigure}{0.45\textwidth}
	\includegraphics[width=\textwidth]{img/planes/intricetcovtraffique.png}
	\caption{Est-ce que c'est de la chance ? Ca a l'air de bien marcher ! }
\end{subfigure}
\end{figure}
\subsection{Analysis}
%
\newpage
% ---- Bibliography ----
%
\begin{thebibliography}{6}
%
